---
title: "Single drug plasma and effect size concentration calculation with stanpumpR"
output: rmarkdown::html_vignette
author: Alexander Clarke
vignette: >
  %\VignetteIndexEntry{Single drug plasma and effect size concentration calculation with stanpumpR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stanpumpR)
library(ggplot2)
```

Define the parameters of the analysis:

```{r}
maximum <- 60
plotRecovery <- FALSE
```

Initialize the drug administration events table. Each row represent either a bolus or a change in the infusion rate.

```{r}
doseTable <- data.frame(
  Drug = c("remifentanil", "remifentanil", "remifentanil"),
  Time = c(0, 0, 30),
  Dose = c(60, 0.15, 0),
  Units = c("mcg", "mcg/kg/min", "mcg/kg/min")
)
```

Initialize an empty events table. The table is used by the Shiny app interface for stanpumpR to display events on the plot.

```{r}
eventTable <- data.frame( Time = double(), Event = character(), Fill = character())
```

Load the pharmacokinetic model parameters. The drug defaults table is loaded for the the specific drug, with default parameters for typical concentration levels, MEAC and emergence/return of spontaneous ventilation.

```{r}
PK <- stanpumpR::getDrugPK(
    drug = "remifentanil",
    weight = 70,
    height = 170,
    age = 50,
    sex = "male",
    stanpumpR::getDrugDefaults('remifentanil')
)
```

Calculate the predicted drug concentrations using simCpCe.

```{r}
output <- stanpumpR::simCpCe(doseTable, eventTable, PK, maximum, plotRecovery)
results <- output['results'][["results"]]
cpce <- results[results$Site == "Plasma"  | results$Site == "Effect Site", ]
```

Plot the output:

```{r}
ggplot(cpce, aes(x=Time, y=Y, group=Site, color=Site)) +
       geom_line() + xlab('Time (minutes)') + ylab('Concentration (ng/ml)')
```
