---
title: "Multiple drug plasma and effect size concentration calculation with stanpumpR"
output: rmarkdown::html_vignette
author: Alexander Clarke
vignette: >
  %\VignetteIndexEntry{Multiple drug plasma and effect size concentration calculation with stanpumpR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stanpumpR)
library(ggplot2)
```

Define the parameters of the analysis:

```{r}
weight = 70
height = 170
age = 50
sex = "male"
maximum = 60
plotRecovery <- FALSE
```

Initialize the drug administration events table. Each row represent either a bolus or a change in the infusion rate.

```{r}
doseTable <- data.frame(
  Drug = c("remifentanil", "remifentanil", "remifentanil","propofol","propofol","propofol"),
  Time = c(0, 0, 40, 0, 0, 30),
  Dose = c(60, 0.15, 0, 200, 150, 0),
  Units = c("mcg", "mcg/kg/min", "mcg/kg/min", "mg", "mcg/kg/min", "mcg/kg/min")
)
```

Initialize an empty events table. The table is used by the Shiny app interface for stanpumpR to display events on the plot.

```{r}
eventTable <- data.frame(Time = double(), Event = character(), Fill = character())
```

Calculate the predicted drug concentrations using simulateDrugsWithCovariates:

```{r}
output <- stanpumpR::simulateDrugsWithCovariates(doseTable, eventTable, weight, height, age, sex, maximum, plotRecovery)
```

Plot the output:

```{r}
for (drug in output) {
  results <- drug['results']$results
  cpce <- results[results$Site == "Plasma" | results$Site == "Effect Site", ]
  f <- ggplot() +
    geom_line(data = cpce, aes(x=Time, y=Y, group=Site, color=Site)) +
    xlab('time (minutes)') + ylab(paste0(drug$Drug,' concentration (', drug$Concentration.Units, ')'))
  print(f)
}
```
